% ============================================================================
% CHAPTER 2: BUSINESS MODEL & REVENUE STRATEGY
% ============================================================================

\chapter{Business Model \& Revenue Strategy}

\section{Four-Tier Service Model}

We offer four complementary services with increasing value and margins:

\subsection{Tier 1: Data Collection}

Raw LiDAR/imagery data sales. \textbf{Price:} BDT 50K-500K per mission. \textbf{Margin:} 35\%. \textbf{Use:} Research, developers, government agencies.

\subsection{Tier 2: Processed Maps}

Orthophotomaps, DTMs, DSMs, 3D models, topographic maps. \textbf{Price:} BDT 200K-1.5M per project. \textbf{Margin:} 50\%. \textbf{Timeline:} 2-4 weeks. \textbf{Use:} Infrastructure, real estate, agriculture.

\subsection{Tier 3: Custom Applications}

Web dashboards, mobile apps, monitoring platforms, APIs. \textbf{Price:} BDT 5-20L per app. \textbf{Margin:} 65-80\%. \textbf{Timeline:} 3-6 months. \textbf{Use:} Farmer advisory, real-time monitoring, decision support.

\subsection{Tier 4: Consulting}

GIS feasibility studies, land use planning, environmental impact, training. \textbf{Price:} BDT 2-10L per engagement. \textbf{Margin:} 70\%. \textbf{Use:} Government, NGOs, major developers.

\section{Revenue Model}

\begin{table}[h!]
    \centering
    \caption{Revenue Model Evolution (Year 1-3)}
    \label{tab:revenue_mix}
    \begin{tabularx}{\textwidth}{l | X | X | X}
        \hline
        \theader{Stream} & \theader{Year 1} & \theader{Year 2} & \theader{Year 3} \\
        \hline
        Project Services & 100\% (30L) & 70\% (67.5L) & 52\% (106L) \\
        \hline
        Data Subscriptions & 0\% & 15\% (14.5L) & 21\% (43L) \\
        \hline
        Custom Apps & 0\% & 10\% (9.6L) & 20\% (41L) \\
        \hline
        Consulting & 0\% & 5\% (4.8L) & 7\% (14L) \\
        \hline
        \textbf{Total Revenue} & \textbf{30L} & \textbf{96.5L} & \textbf{204L} \\
        \hline
    \end{tabularx}
\end{table}

\textbf{Key Insight:} By Year 3, 48\% of revenue is recurring (subscriptions + apps), providing stability and higher margins.

\section{Target Customer Segments}

\subsection{Agriculture (Primary Market)}

\textbf{Market:} 10M small farmers, 500K medium farms, 50K large farms

\textbf{Problems We Solve:}
\begin{itemize}
    \item Yield uncertainty → Crop health monitoring via NDVI
    \item Water waste → Irrigation optimization from topography
    \item Pest/disease outbreaks → Early detection via thermal imagery
    \item Poor decisions → Yield prediction via Data Science models
\end{itemize}

\textbf{Channel:} NGO partnerships (BRAC reaching 100M+ people, ASA 2M+ members)

\textbf{Economic Model:} Farmer pays BDT 5-8K/year. We pay NGO 15-20\% commission. NGO gets new revenue, we get distribution.

\subsection{Government}

\textbf{Agencies:} Ministry of Land, LGED, Disaster Management, Urban Development

\textbf{Budget:} BDT 500+ crores annually for geospatial work

\textbf{Problems:} Outdated survey data (25+ years old), manual slow processes, limited disaster planning data

\subsection{Real Estate \& Construction}

\textbf{Market:} 50+ major developers, 200+ construction companies, BDT 50,000+ crores annual development

\textbf{Problems:} Site selection, accurate land measurement, infrastructure impact, 3D visualization, feasibility analysis

\subsection{NGOs \& Environment}

\textbf{Organizations:} BRAC (10M beneficiaries), ASA (2M members), Practical Action, environmental groups

\textbf{Problems:} Limited evidence data, difficulty monitoring large areas, farmer-level insights, impact measurement

\section{Pricing Strategy: Value-Based Model}

We price based on value delivered, not cost-plus:

\begin{table}[h!]
    \centering
    \caption{Value-Based Pricing Examples}
    \label{tab:pricing_examples}
    \begin{tabularx}{\textwidth}{l | X | X}
        \hline
        \theader{Customer Type} & \theader{Value Driver} & \theader{Price} \\
        \hline
        Small Farmer (50 ha) & Cost recovery + yield gains & BDT 1.5L \\
        \hline
        Large Agri Company (1,000 ha) & Cost + yield optimization & BDT 4-6L \\
        \hline
        Government (10,000 ha region) & Cost + volume discount & BDT 40-60L \\
        \hline
        Real Estate Developer & Cost + IP + 3D visualization & BDT 10-15L \\
        \hline
        NGO Partner (farmer programs) & Cost + social impact & BDT 1.5-2.5L \\
        \hline
    \end{tabularx}
\end{table}

\section{NGO Partnership Model (Key Differentiator)}

Our unique competitive advantage:

\begin{enumerate}
    \item \textbf{We build farmer apps:} Yield prediction, disease detection, irrigation planning
    \item \textbf{NGOs distribute:} BRAC/ASA field officers already visit farmers monthly
    \item \textbf{Revenue sharing:} Farmer pays BDT 5K-10K/year, NGO gets 15-20\% commission
    \item \textbf{Farmer benefits:} 5-15\% yield improvement = BDT 50-300K value (payback in 3-12 weeks)
    \item \textbf{NGO benefits:} New revenue stream (BDT 750-2K per farmer annually)
    \item \textbf{We benefit:} 80-85\% margin, unlimited scale via NGO network
\end{enumerate}

\textbf{Why This Works:}
\begin{itemize}
    \item Farmers trust NGOs (40+ year relationships)
    \item NGOs have monthly farmer contact (training, credit, services)
    \item No competing providers (only we are doing this)
    \item Economics make sense for all parties
    \item Farmer adoption proof exists (127K already using drones)
\end{itemize}

\section{Business Model Sustainability}

\begin{itemize}
    \item \textbf{Recurring Revenue:} 48\% by Year 3 (stability)
    \item \textbf{Margin Improvement:} 7\% Year 1 → 51\% Year 2 → 67\% Year 3
    \item \textbf{Scalability:} Apps scale infinitely after initial development
    \item \textbf{Diversification:} No single customer >10\% of revenue
    \item \textbf{Resilience:} If projects decline, subscriptions provide base revenue
\end{itemize}

% ============================================================================
% END OF CHAPTER 2
% ============================================================================
